\bf\mftitle

### 2011-03-02 doc/jInfer/paper/paper.tex
first try

\documentclass[a4paper,10pt,oneside]{article}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tgpagella}
%\usepackage[scale=0.9]{tgcursor}
%\usepackage[scale=0.9]{tgheros}
\usepackage{xstring}
\usepackage{wrapfig}

@@

\def\mftitle{jInfer TwoStepSimplifier Module Description}
\def\mfauthor{Michal Klempa, Mário Mikula, Robert Smetana, Michal Švirec, Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková, Ph.D., Martin Nečaský, Ph.D.}
\def\mfplacedate{Praha, 2011}
\title{\bf\mftitle}
\author{\mfauthor \\ Advisors: \mfadvisor}
\date{\mfplacedate}

@@

\begin{document}

\maketitle
\noindent Target audience: developers willing to extend jInfer, researchers willing to implement own inference methods.

\noindent \emph{Note: we use the term \textbf{inference} for the act of creation of schema throughout this and other jInfer documents.}

@@

\nocite{*}
\newpage
\bibliographystyle{alpha}
\bibliography{literature}

>>>>

\documentclass[a4paper,10pt,oneside,twocolumn]{article}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tgpagella}
%\usepackage[scale=0.9]{tgcursor}
%\usepackage[scale=0.9]{tgheros}
\usepackage{xstring}
\usepackage{wrapfig}

@@

\def\mftitle{jInfer XML schema inference framework}
\def\mfauthor{Michal Klempa, Mário Mikula, Robert Smetana, Michal Švirec, Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková, Ph.D., Martin Nečaský, Ph.D.}
\def\mfplacedate{Praha, 2011}
\title{\bf\mftitle}
\author{\mfauthor \\ Advisors: \mfadvisor}
\date{\mfplacedate}

@@

\begin{document}
\maketitle

\abstract
Today, many algorithms solving XML schema inference problem exist.
None of them is widely used by public to practically solve the problem.
This is because the lack of simple user interface to algorithms.
We present NetBeans (\cite{netbeans}) based pluggable framework to fill this gap.
Thus enabling people dealing with XML in practice to obtain schema for their documents by following simple steps, without need to read and understand theoretical aspects.
We hope our solution will boost usage of XML schemas in practice, since creating schema for existing set of documents will be more effordable (one doesn't have to write one by hand).

\section*{Introduction}
Although many algorithms (\cite{ahonen, Bex:2006:ICD:1182635.1164139, Bex:2007:IXS:1325851.1325964, 1802522, vyhnanovska})

\section*{Related work}

%\nocite{*}
\newpage
\bibliographystyle{alpha}
\bibliography{literature}
\end{document}

@@
